Analyzing Information Transfer from Heterogeneous Sources via Precise High-dimensional Asymptotics

### 2021-07-22 revision_journal/intro.tex
wip

We consider a high-dimensional setting (e.g., \citet{hastie2019surprises}) where the sample size $n_i$ increases with $p$ proportionally by a constant factor.
Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
We assume that
\begin{align}
    x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_rvm}
\end{align}
where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition. 
We focus on the so called \textit{underparametrized} setting for task two where $n_2 > \rho p$ for a constant $\rho > 1$ whereas for task one $n_1$ can be smaller than $p$.
%A distinction between our setup and \citet{hastie2019surprises} is that we 
See Section \ref{sec_data} for the precise assumptions underlying the above data model.

>>>>

We consider a high-dimensional setting (e.g., \citet{hastie2019surprises}) where the sample size $n_i$ increases with $p$ to infinity proportionally by a constant factor.
Let $\Sigma^{(i)} \in \real^{p\times p}$ be a deterministic positive semidefinite matrix.
We assume that
\begin{align}
    x_j^{(i)} = \big(\Sigma^{(i)}\big)^{1/2} z_{j}^{(i)}, \text{ for any } j = 1,\dots,n_i, \label{eq_rvm}
\end{align}
where $z_j^{(i)}$ consists of independent and identical entries sampled from a distribution that has zero mean, unit variance, and satisfies certain bounded moment condition. 
We focus on the so called \textit{underparametrized} setting for task two where $n_2 > \rho p$ for a constant $\rho > 1$ whereas for task one $n_1$ can be smaller than $p$.
%A distinction between our setup and \citet{hastie2019surprises} is that we 
See Section \ref{sec_data} for the precise assumptions underlying the above data model.

### 2021-07-22 revision_journal/main_arxiv.tex
intro wip
wip

\usepackage{macro_math}
\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX
\usepackage{graphicx, subcaption}
\usepackage[export]{adjustbox}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage[hidelinks]{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage[utf8]{inputenc} %
\usepackage{caption,subcaption}

%\newcommand{\citet}{\cite}

\begin{document}

	\title{Estimating Information Transfer from Different Sources in High-dimensional Linear Regression}

    \author{Fan Yang\thanks{University of Pennsylvania. fyang75@wharton.upenn.edu}\and Hongyang R. Zhang \thanks{Northeastern University. ho.zhang@northeastern.edu. Part of this work was done while the author was at UPenn.}\and Sen Wu\thanks{Stanford University. senwu@stanford.edu}\and Weijie J. Su \thanks{University of Pennsylvania. suw@wharton.upenn.edu}\and Christopher R\'e\thanks{Stanford University. chrismre@stanford.edu}}

	\maketitle
	\input{abstract}
	\input{intro}
	\input{setup}
	\input{results}
	\input{exp}
    \input{multitask.tex}
	\input{conclusions}
	\bibliographystyle{plainnat}
	\bibliography{rf,rf_tl,ref_mtl}

>>>>

\usepackage{macro_math}
\usepackage[us,12hr]{datetime} % `us' makes \today behave as usual in TeX/LaTeX
\usepackage{graphicx, subcaption}
\usepackage[export]{adjustbox}
\usepackage{subfloat}
\usepackage[T1]{fontenc}    %
\usepackage{nicefrac}       %
\usepackage{microtype}      %
\usepackage[hidelinks]{hyperref}
\hypersetup{colorlinks,linkcolor={blue},citecolor={blue},urlcolor={red}}
\usepackage{macro_fan}
\usepackage{stmaryrd}
\usepackage[utf8]{inputenc} %
\usepackage{caption,subcaption}
\DeclareMathSizes{10}{10}{7}{4}
%\newcommand{\citet}{\cite}
%\catcode`^=\active
%\newcommand^[1]{\ensuremath{\smallp{\scriptscriptstyle #1}}}
\begin{document}

	\title{Analyzing Information Transfer from Heterogeneous Sources via Precise High-dimensional Asymptotics}

    %\author{Fan Yang\thanks{University of Pennsylvania. fyang75@wharton.upenn.edu}\and Hongyang R. Zhang \thanks{Northeastern University. ho.zhang@northeastern.edu. Part of this work was done while the author was at UPenn.}\and Sen Wu\thanks{Stanford University. senwu@stanford.edu}\and Weijie J. Su \thanks{University of Pennsylvania. suw@wharton.upenn.edu}\and Christopher R\'e\thanks{Stanford University. chrismre@stanford.edu}}

	\maketitle
	\input{abstract}
	\input{intro}
	\input{setup}
	\input{results}
	\input{exp}
    \input{multitask}
	\input{conclusions}
	\bibliographystyle{plainnat}
	\bibliography{rf,rf_tl,ref_mtl}
